---
title: "Pre-Analytic Cleaning+Imputation"
output: html_document
date: "2025-06-17"
---

To date this is the capabilities of this code
      Main parent group diagnosis
      Dim anxiety for young participant. 
      Looks for diagnosis
      Creates lifetime diagnosis based on current
      Creates onset of disorder variable
      Has some hospital information on diagnosis

##Need to do
Create value for different parent diagnoses
Need lifetime baseline diagnosis of disorders

Make dim and antecedent variables
  dimdep dimanx scaredytot dimafflaby dimafflab dimirrit dimpsych dimbs dimsleep
  antanx antafflab antpsych antbs antsleep antcog antdep antno 


##Things of Note
Maybe some weird diagnosis variables? Like SAD.
Observations always have one observation that is NA?

## Library
```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(haven); library(dplyr); library(tidyr); library(readr); library(readxl); library(data.table); library(stringr); library(purrr)  # Data manipulation & import
library(lme4); library(lmerTest); library(coxme); library(survival); library(broom); library(MuMIn); library(lsmeans)  # Modeling & statistics
library(pander); library(apaTables); library(flextable); library(officer); library(webshot2)  # Tables & reporting
library(ggplot2)  # Plotting
library(fuzzyjoin)  # Joins
library(survminer)
library(plotly)
```

## Load CSV
```{r}
# setwd("C:/Users/hubshmz/Documents/Code/git/data")  # FORBOW computer
setwd("C:/Users/zachh/Documents/Code/git/Data")  # Laptop
# setwd("C:/Users/zacha/Documents/RStudio/forbow/git/Data/ESCAP") # Tupper Windows Comp
# setwd("C:/Users/zacha/Documents/forbow/code/git") # Home Computer

##Do unlabeled, ZACH FORBOW report from the master database. 
FOR <- read.csv("FORBOWMasterDatabase.csv", header=TRUE, fileEncoding="latin1")
```



##Parent Diagnosis and Family Risk
```{r}
FOR$fid <- substr(FOR$subject_id, 5, 7)
FOR$iid <- substr(FOR$subject_id, 8, 11)
FOR_P <- FOR %>%
  filter(str_detect(subject_id, "F[1-3]|f[1-3]|M[1-3]|m[1-3]|\\$R"))


FOR_P <- FOR_P %>%
  mutate(group = case_when(
    mdx == 4 ~ 1,
    mdx %in% c(2, 3) ~ 2,
    mdx == 1 ~ 3,
    mdx == 0 ~ 0,
    fdx == 4 ~ 1, 
    fdx %in% c(2,3) ~ 2,
    fdx == 1 ~ 3,
    fdx == 0 ~ 0,
    TRUE ~ NA_real_
  ))

FOR_P <- FOR_P %>%
  group_by(subject_id) %>%
  mutate(
    group = {
      g <- group[is.na(time_point)]
      if (length(g) == 0 || is.na(g[1])) 0 else g[1]
    }
  ) %>%
  ungroup()


table(FOR_P$medul)

fid_group_list <- FOR_P %>%
  group_by(fid) %>%
  summarise(
    group = if (all(is.na(group))) NA_real_ else max(group, na.rm = TRUE),
    medul_parent = if (all(is.na(medul))) NA_real_ else max(medul, na.rm = TRUE),
    fedul_parent = if (all(is.na(fedul))) NA_real_ else max(fedul, na.rm = TRUE),
    .groups = "drop"
  )

#Join back into full data set
FOR <- FOR %>%
  left_join(fid_group_list, by = "fid")
```

#Demographic Information

###Sex/Age
```{R}
FOR <- FOR %>%
  group_by(subject_id) %>%
  mutate(dob = dob[which(is.na(time_point))][1]) %>%
  ungroup()
FOR <- FOR %>%
  group_by(subject_id) %>%
  mutate(sex = sex[which(is.na(time_point))][1]) %>%
  ungroup()
FOR <- FOR %>%
  mutate(sex = case_when(
    sex == 1 ~ 0,
    sex == 2 ~ 1
  ))
FOR <- FOR %>%
  group_by(subject_id) %>%
  filter(all(!is.na(dob) & dob != "")) %>%  # Keep only groups where *all* dob are not missing or empty
  ungroup()
invalid_si <- c("9999999888", "9999999998")
FOR <- FOR %>%
  filter(!subject_id %in% invalid_si)

FOR$assessment_date <- as.Date(FOR$assessment_date)
FOR$dob <- as.Date(FOR$dob)
FOR$age_days <- FOR$assessment_date - FOR$dob
FOR$age <- as.numeric(FOR$age_days) / 365.25
```


###SES
```{r}
library(dplyr)

FOR <- FOR %>%
  mutate(
    # initialize SES domain flags
    sesmedul   = as.integer(medul_parent   > 2.5 & medul_parent   < 9),
    sesfedul   = as.integer(fedul_parent   > 2.5 & fedul_parent   < 9),
    sesown     = as.integer(oresown == 1),
    sesincome  = as.integer(oincome > 3.5 & oincome < 9),

    # correct the 43 coding error in household rooms
    ohomerooms = ifelse(ohomerooms == 43, 3, ohomerooms),

    # bedrooms-to-person ratio
    bpratio    = ohomerooms / ohousepers,
    sesbpratio = as.integer(bpratio > 0.9 & bpratio < 9),

    # total SES
    ses = sesmedul + sesfedul + sesown + sesincome + sesbpratio
  )
```

#Dimension Creation
Creates dimdep dimanx scaredytot dimafflaby dimafflab dimirrit dimpsych dimbs dimsleep 
### Dimension Anxiety
```{r}
Scared_C_Variables <- paste0("scared_child_", 1:41)
Scared_P_Variables <- paste0("scared_parent_", 1:41)
FOR <- FOR %>%
  # Recode 9s to NA
  mutate(across(all_of(Scared_C_Variables), ~na_if(.x, 9))) %>%
  mutate(across(all_of(Scared_P_Variables), ~na_if(.x, 9))) %>%
  
  # Compute total scores
  mutate(
    Scared_C_Total = rowSums(across(all_of(Scared_C_Variables)), na.rm = TRUE),
    Scared_P_Total = rowSums(across(all_of(Scared_P_Variables)), na.rm = TRUE)
  ) %>%
  
  # Standardize total scores
  mutate(
    Scared_C_Total_z = as.numeric(scale(Scared_C_Total)),
    Scared_P_Total_z = as.numeric(scale(Scared_P_Total))
  )

Scas_C_Variables <- paste0("scas_child_", 1:44)
Scas_P_Variables <- paste0("scas_parent_", 1:38)

remove_indices <- c(11, 17, 26, 31, 38, 43)
Scas_C_Variables <- Scas_C_Variables[-remove_indices]


FOR <- FOR %>%
  # Recode 9s to NA
  mutate(across(all_of(Scas_C_Variables), ~na_if(.x, 9))) %>%
  mutate(across(all_of(Scas_P_Variables), ~na_if(.x, 9))) %>%
  
  # Compute total scores
  mutate(
    Scas_C_Total = rowSums(across(all_of(Scas_C_Variables)), na.rm = TRUE),
    Scas_P_Total = rowSums(across(all_of(Scas_P_Variables)), na.rm = TRUE)
  ) %>%
  
  # Standardize total scores
  mutate(
    Scas_C_z = as.numeric(scale(Scas_C_Total)),
    Scas_P_z = as.numeric(scale(Scas_P_Total))
  )

FOR <- FOR %>%
  # SCAS dimanx
  mutate(dimanx = rowMeans(across(c(Scas_C_z, Scas_P_z, Scared_C_Total_z, Scared_P_Total_z)), na.rm = TRUE)) 
```

###Dimension Depression
```{r}

```

#Maltretmeant/Bullying

###Malt variables
Rudolf has ceca/jvq valid for malt creation... isn't in redcap though so unsure
```{r}
library(dplyr)

##Creating Maltreatment Variables
FOR <- FOR %>%
  mutate(
    ## Physical maltreatment
    maltp = as.integer(
      rowSums(across(c(jvq10_cv, jvq10_pv,
                      jvq11_cv, jvq11_pv),
                     ~ . == 2), na.rm = TRUE) > 0
    ),
    ## Emotional maltreatment
    malte = as.integer(
      rowSums(across(c(jvq12_cv, jvq12_pv),
                     ~ . == 2), na.rm = TRUE) > 0 |
      cecatorment11 == 1
    ),
    ## Neglect
    maltn = as.integer(
      rowSums(across(c(jvq13_cv, jvq13_pv,
                      jvq41_cv, jvq41_pv,
                      jvq42_cv, jvq42_pv,
                      jvq43_cv, jvq43_pv,
                      jvq44_cv, jvq44_pv,
                      jvq45_cv, jvq45_pv),
                     ~ . == 2), na.rm = TRUE) > 0 |
      cecabasneed11 == 1 |
      cecabasneed16 == 1
    ),
    ## Custody disruption
    custodydisp = as.integer(
      rowSums(across(c(jvq14_cv, jvq14_pv), ~ . == 2), na.rm = TRUE) > 0
    ),
    ## Sexual maltreatment
    malts = as.integer(
      rowSums(across(c(jvq25_cv, jvq25_pv,
                      jvq26_cv, jvq26_pv,
                      jvq28_cv, jvq28_pv),
                     ~ . == 2), na.rm = TRUE) > 0 |
      cecaunwsex11 == 1 |
      cecaunwsex16 == 1
    ),

    ## Violence exposure
    maltv = as.integer(
      rowSums(across(c(jvq32_cv, jvq32_pv,
                      jvq33_cv, jvq33_pv,
                      jvq34_cv, jvq34_pv,
                      jvq35_cv, jvq35_pv,
                      jvq36_cv, jvq36_pv,
                      jvq37_cv, jvq37_pv),
                     ~ . == 2), na.rm = TRUE) > 0 |
      cecafreqarg11 == 1 |
      cecafreqarg16 == 1
    )
  )



##Overall maltreatment at that visit
FOR <- FOR %>%
  mutate(
    malt = as.integer(maltp == 1 | malte == 1 | malts == 1 | maltn == 1),
    #Have malt include violence too
    bmalt = as.integer(malt == 1 | maltv == 1)
  )


##Create the lifetime maltreatment variable
FOR <- FOR %>%
  group_by(subject_id) %>%
  mutate(
    ## malt subtype lifetime
    maltp_ever = as.integer(any(maltp == 1, na.rm = TRUE)),
    malte_ever = as.integer(any(malte == 1, na.rm = TRUE)),
    maltn_ever = as.integer(any(maltn == 1, na.rm = TRUE)),
    malts_ever = as.integer(any(malts == 1, na.rm = TRUE)),
    maltv_ever = as.integer(any(maltv == 1, na.rm = TRUE)),
    custody_ever = as.integer(any(custodydisp == 1, na.rm = TRUE)),

    ## overall malt (physical, emotional, neglect, sexual)
    malt_ever = as.integer(
      any(maltp == 1 | malte == 1 | malts == 1 | maltn == 1, na.rm = TRUE)
    ),

    ## broadened malt including violence
    bmalt_ever = as.integer(
      any(maltp == 1 | malte == 1 | malts == 1 | maltn == 1 | maltv == 1, na.rm = TRUE)
    )
  ) %>%
  ungroup()
```

###Bully
Generates bullying_ever. Which finds out if someone hsa either previously or currently is experiencing bullying.
```{r}
FOR <- FOR %>%
  mutate(
    bullying = case_when(
      obully == 4 ~ 1L,
      obully == 3 ~ 1L,
      obully == 2 & obullserv %in% c(3, 4) ~ 1L,
      obully > 4.5 ~ NA_integer_,
      age < 4.99 ~ NA_integer_,
      TRUE ~ 0L
    )
  )

FOR <- FOR %>%
  mutate(
    cyber = case_when(
      ocyber1 > 1.5 & ocyber1 < 8 ~ 1L,
      ocyber2 > 1.5 & ocyber2 < 8 ~ 1L,
      ocyber3 > 1.5 & ocyber3 < 8 ~ 1L,
      TRUE ~ 0L
    )
  )

##This fidns if someone previously was bullied
FOR <- FOR %>%
  arrange(subject_id, time_point) %>%
  group_by(subject_id) %>%
  mutate(bullying_ever = cummax(replace(bullying, is.na(bullying), 0))) %>%
  ungroup()
```

###Adveristy
Creates adversity measure. If an individual was bullied, has experiened maltreatment, or a custody dispute, then they get adversity as 1.
```{r}
FOR <- FOR %>%
  mutate(
    adversity = case_when(
      malt > 9 | bullying > 9 ~ NA_integer_,
      bmalt == 1 | custodydisp == 1 | bullying == 1 ~ 1L,
      TRUE ~ 0L
    )
  )
```

###Polye
```{r}
FOR <- FOR %>%
  mutate(
    rsesmedul    = ifelse(sesmedul == 1, 0L, ifelse(sesmedul == 0, 1L, NA_integer_)),
    rsesfedul    = ifelse(sesfedul == 1, 0L, ifelse(sesfedul == 0, 1L, NA_integer_)),
    rsesown      = ifelse(sesown == 1, 0L, ifelse(sesown == 0, 1L, NA_integer_)),
    rsesincome   = ifelse(sesincome == 1, 0L, ifelse(sesincome == 0, 1L, NA_integer_)),
    rsesbpratio  = ifelse(sesbpratio == 1, 0L, ifelse(sesbpratio == 0, 1L, NA_integer_))
  )

FOR <- FOR %>% 
  mutate(
    polye      = rowMeans(across(c(malts, maltp, malte, maltn, maltv, bullying, rsesmedul, rsesfedul, rsesown, rsesincome)), na.rm = TRUE),
    polyvicte  = rowMeans(across(c(malts, maltp, malte, maltn, maltv, bullying)), na.rm = TRUE),
    polysese   = rowMeans(across(c(rsesmedul, rsesfedul, rsesown, rsesincome)), na.rm = TRUE),
    polyv      = rowMeans(across(c(malts, maltp, malte, maltn, maltv, bullying, cyber)), na.rm = TRUE),
    c4polyv    = case_when(polyv > 3.5 & polyv < 9 ~ 1L, TRUE ~ 0L),
    zpolye     = (polye - mean(polye, na.rm = TRUE)) / sd(polye, na.rm = TRUE)
  )
```

#Diagnosis
###Current Diagnosis
```{r}
### List of FORBOW Diagnoses


KSADS_ALL <- c('MDD', 'DEP', 'Dysthy', 'BP', 'BPI', 'BPII', 'MOOD',
               'Psychosis', 'iPsychosis', 'SCZ', 'SchAff',
               'SUD', 'Alc', 'Can', 'Dependence',
               'Anx', 'Panic', 'OthAnx', 'GAD', 'SocialP', 'PTSD', 'Agora', 'SpecificP', 'OCD', 'SAD',
               'ADHD', 'ODD', 'Conduct', 'Disrupt',
               'ED', 'EDNOS', 'Anor', 'Bulims',
               'Autism', 'ASD', 'Tic', 'Touret',
               'LD', 'LDs', 'LDg',
               'DMDD', 'Sleep',
               'Borderline', 'Antisocial', 'PersonalityDisord')


##ccMDD = 0
##ccDEP = 0
##ccPsychosis = 0
##cciPsychosis = 0
##ccSCHZ = 0
##ccSchAff = 0 
##ccBPD = 0
##ccBPDI = 0
##ccBPDII = 0
##ccBorderline = 0
##ccAntisocial = 0
##ccANX = 0
##ccPanic = 0
##ccOthAnx = 0
##ccGAD = 0
##ccSocialP = 0 
##ccAgora = 0
##ccPTSD = 0 
##ccOCD = 0
##ccSAD = 0
##ccSpecificP = 0
##ccSUD = 0
##ccCan = 0
##ccAlc = 0
##ccDependence = 0
##ccADHD = 0
##ccODD = 0
##ccConduct = 0
##ccDisrupt = 0
##ccED = 0
##ccAnor = 0
##ccBulim = 0
##ccEDNOS = 0
##ccAutism = 0
##ccASD = 0
##ccTic = 0
##ccTouret = 0
##ccLD = 0
##ccLDs = 0
##ccLDg = 0
##ccSleep
##ccDMDD
##ccDysthy = 0

###Varaibles we have but are unused?
#ccPBPD = 0
#ccPDD = 0
#ccAdjAnx = 0



##Clinical Diagnosis from Consesus
Diagnosis_vars <- paste0("cd_c_dx_", 1:10)

#Depression
FOR$ccMDD <- 0
FOR$ccDEP <- 0 
FOR$ccDysthy <- 0
for (i in 1:10) {
  dx_col <- paste0("cd_c_dx_", i)
  conf_col <- paste0("cd_c_confirmed_", i)
  text_col <- paste0("cd_c_dx_other_", i)
  rows_to_update <- FOR[[dx_col]] == 1 & FOR[[conf_col]] != 0
  FOR$ccMDD[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(1,2,3) & FOR[[conf_col]] != 0
  FOR$ccDEP[rows_to_update] <- 1
  rows_to_update <- FOR[[text_col]] %in% c("depress", "Depress", "Major Depress", "major depress") & FOR[[conf_col]] != 0
  FOR$ccDEP[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(2) & FOR[[conf_col]] != 0
  FOR$ccDysthy[rows_to_update] <- 1
}

#Mania
FOR$ccBP <- 0
FOR$ccBPI <- 0
FOR$ccBPII <- 0
for (i in 1:10) {
  dx_col <- paste0("cd_c_dx_", i)
  conf_col <- paste0("cd_c_confirmed_", i)
  text_col <- paste0("cd_c_dx_other_", i)
  rows_to_update <- FOR[[dx_col]] %in% c(4, 5,6,7) & FOR[[conf_col]] != 0
  FOR$ccBP[rows_to_update] <- 1
  rows_to_update <- FOR[[dx_col]] %in% c(4) & FOR[[conf_col]] != 0
  FOR$ccBPI[rows_to_update] <- 1
  rows_to_update <- FOR[[dx_col]] %in% c(5) & FOR[[conf_col]] != 0
  FOR$ccBPI[rows_to_update] <- 1
  rows_to_update <- FOR[[text_col]] %in% c("Mania", "mania", "Bipolar", "bipolar") & FOR[[conf_col]] != 0
  FOR$ccBP[rows_to_update] <- 1
}
table(FOR$ccBP)
table(FOR$ccBPI)
table(FOR$ccBPII)


##Psychosis
FOR$ccPsychosis <- 0
FOR$cciPsychosis <- 0
FOR$ccSCZ <- 0
FOR$ccSchAff <- 0
for (i in 1:10) {
  dx_col <- paste0("cd_c_dx_", i)
  conf_col <- paste0("cd_c_confirmed_", i)
  rows_to_update <- FOR[[dx_col]] %in% c(8,9,10,11,12,13,14) & FOR[[conf_col]] != 0 
  FOR$ccPsychosis[rows_to_update] <- 1
  rows_to_update <- FOR[[dx_col]] %in% c(8) & FOR[[conf_col]] != 0 
  FOR$ccSCZ[rows_to_update] <- 1
  rows_to_update <- FOR[[dx_col]] %in% c(9) & FOR[[conf_col]] != 0 
  FOR$ccSchAff[rows_to_update] <- 1
}

#Personality
FOR$ccBorderline <- 0
FOR$ccAntisocial <- 0
FOR$ccPersonalityDisord <- 0
for (i in 1:10) {
  dx_col <- paste0("cd_c_dx_", i)
  conf_col <- paste0("cd_c_confirmed_", i)
  text_col <- paste0("cd_c_dx_other_", i)
  rows_to_update <- FOR[[dx_col]] %in% c(25) & FOR[[conf_col]] != 0 
  FOR$ccBorderline[rows_to_update] <- 1
  rows_to_update <- FOR[[text_col]] %in% c("orderline") & FOR[[conf_col]] != 0
  FOR$ccBorderline[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(26) & FOR[[conf_col]] != 0 
  FOR$ccAntisocial[rows_to_update] <- 1
  rows_to_update <- FOR[[text_col]] %in% c("ntisocial") & FOR[[conf_col]] != 0
  FOR$ccAntisocial[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(70,71,72,73,74,75,76,77,78,79,80) & FOR[[conf_col]] != 0
  FOR$ccPersonalityDisord[rows_to_update] <- 1
  rows_to_update <- FOR[[text_col]] %in% c("personality", "Personality", "antisocial", "Antisocial", "orderline") &FOR[[conf_col]] != 0
  FOR$ccPersonalityDisord[rows_to_update] <- 1
}

#Substance Use
FOR$ccAlc <- 0
FOR$ccCan <- 0
FOR$ccSUD <- 0
FOR$ccDependence <- 0
for (i in 1:10) {
  dx_col <- paste0("cd_c_dx_", i)
  conf_col <- paste0("cd_c_confirmed_", i)
  rows_to_update <- FOR[[dx_col]] %in% c(38,39) & FOR[[conf_col]] != 0 
  FOR$ccAlc[rows_to_update] <- 1
  rows_to_update <- FOR[[dx_col]] %in% c(40,41) & FOR[[conf_col]] != 0 
  FOR$ccCan[rows_to_update] <- 1
  rows_to_update <- FOR[[dx_col]] %in% c(38,39,40,41,42,43) & FOR[[conf_col]] != 0 
  FOR$ccSUD[rows_to_update] <- 1
  rows_to_update <- FOR[[dx_col]] %in% c(39,41,43) & FOR[[conf_col]] != 0 
  FOR$ccDependence[rows_to_update] <- 1
}

#Anxiety Disorders
FOR$ccAnx <- 0
FOR$ccSAD <- 0  #Why is SAD 15 and why is anxiety within SAD?
FOR$ccSpecificP <- 0
FOR$ccSocialP <- 0 
FOR$ccAgora <- 0
FOR$ccPanic <- 0
FOR$ccGAD <- 0
FOR$ccOCD <- 0
FOR$ccPTSD <- 0
FOR$ccOthAnx <- 0
for (i in 1:10) {
  dx_col <- paste0("cd_c_dx_", i)
  conf_col <- paste0("cd_c_confirmed_", i)
  text_col <- paste0("cd_c_dx_other_", i)
  
  rows_to_update <- FOR[[dx_col]] %in% c(15,16,17,18,19,20,21,22,24) & FOR[[conf_col]] != 0    #Anxiety Disorders
  FOR$ccAnx[rows_to_update] <- 1
  rows_to_update <- FOR[[text_col]] %in% c("nxiety", "GAD", "Mutism", "mutism") & FOR[[conf_col]] != 0    #Anxiety disorders
  FOR$ccAnx[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(15) & FOR[[conf_col]] != 0    #SAD?
  FOR$ccSAD[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(16) & FOR[[conf_col]] != 0   #Specific P
  FOR$ccSpecificP[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(17) & FOR[[conf_col]] != 0   #Social P
  FOR$ccSocialP[rows_to_update] <- 1
  rows_to_update <- FOR[[text_col]] %in% c("Social") & FOR[[conf_col]] != 0 #Social P
  FOR$ccSocialP[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(18) & FOR[[conf_col]] != 0        #AGORA
  FOR$ccAgora[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(19) & FOR[[conf_col]] != 0       #Panic
  FOR$ccPanic[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(20) & FOR[[conf_col]] != 0       #GAD
  FOR$ccGAD[rows_to_update] <- 1
  rows_to_update <- FOR[[text_col]] %in% c("GAD") & FOR[[conf_col]] != 0 #GAD
  FOR$ccGAD[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(21) & FOR[[conf_col]] != 0       #OCD
  FOR$ccOCD[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(22) & FOR[[conf_col]] != 0       #PTSD
  FOR$ccPTSD[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(24) & FOR[[conf_col]] != 0       #OthAnx
  FOR$ccOthAnx[rows_to_update] <- 1
}

#Eating Disorder
FOR$ccAnor <- 0
FOR$ccBulims <- 0
FOR$ccEDNOS <- 0
FOR$ccED <- 0
for (i in 1:10) {
  dx_col <- paste0("cd_c_dx_", i)
  conf_col <- paste0("cd_c_confirmed_", i)
  text_col <- paste0("cd_c_dx_other_", i)
  
  rows_to_update <- FOR[[dx_col]] %in% c(28) & FOR[[conf_col]] != 0 
  FOR$ccAnor[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(29) & FOR[[conf_col]] != 0 
  FOR$ccBulims[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(30) & FOR[[conf_col]] != 0 
  FOR$ccEDNOS[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(28,29,30) & FOR[[conf_col]] != 0 
  FOR$ccED[rows_to_update] <- 1
  rows_to_update <- FOR[[text_col]] %in% c("Eating","eating","Pica", "pica") & FOR[[conf_col]] != 0 
  FOR$ccED[rows_to_update] <- 1
}

##Development
FOR$ccADHD <- 0
FOR$ccODD <- 0
FOR$ccConduct <- 0
FOR$ccDisrupt <- 0
for (i in 1:10) {
  dx_col <- paste0("cd_c_dx_", i)
  conf_col <- paste0("cd_c_confirmed_", i)
  text_col <- paste0("cd_c_dx_other_", i)
  
  rows_to_update <- FOR[[dx_col]] %in% c(31,32,33) & FOR[[conf_col]] != 0    #ADHD
  FOR$ccADHD[rows_to_update] <- 1
  rows_to_update <- FOR[[text_col]] %in% c("ADHD") & FOR[[conf_col]] != 0 
  FOR$ccADHD[rows_to_update] <- 1
    
  rows_to_update <- FOR[[dx_col]] %in% c(34) & FOR[[conf_col]] != 0         #ODD
  FOR$ccODD[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(35) & FOR[[conf_col]] != 0        #Conduct
  FOR$ccConduct[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(34,35) & FOR[[conf_col]] != 0        #Disruptive Disorder
  FOR$ccDisrupt[rows_to_update] <- 1
  rows_to_update <- FOR[[text_col]] %in% c("isruptive") & FOR[[conf_col]] != 0 
  FOR$ccDisrupt[rows_to_update] <- 1
}

#Neuro
FOR$ccTic <- 0
FOR$ccTouret <- 0
FOR$ccAutism <- 0
FOR$ccASD <- 0
for (i in 1:10) {
  dx_col <- paste0("cd_c_dx_", i)
  conf_col <- paste0("cd_c_confirmed_", i)
  text_col <- paste0("cd_c_dx_other_", i)
  
  rows_to_update <- FOR[[dx_col]] %in% c(36,37) & FOR[[conf_col]] != 0    #TIC
  FOR$ccTic[rows_to_update] <- 1
  rows_to_update <- FOR[[text_col]] %in% c("Tic", "tic", "ouret") & FOR[[conf_col]] != 0 
  FOR$ccTic[rows_to_update] <- 1
    
  rows_to_update <- FOR[[dx_col]] %in% c(36) & FOR[[conf_col]] != 0         #Touret
  FOR$ccTouret[rows_to_update] <- 1
  rows_to_update <- FOR[[text_col]] %in% c("ouret") & FOR[[conf_col]] != 0 
  FOR$ccTouret[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(44) & FOR[[conf_col]] != 0        #Autism
  FOR$ccAutism[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(44,45, 46) & FOR[[conf_col]] != 0        #Autism Spectrum
  FOR$ccASD[rows_to_update] <- 1
}

#Learning Disabilities
FOR$ccLD <- 0
FOR$ccLDs <- 0
FOR$ccLDg <- 0
for (i in 1:10) {
  dx_col <- paste0("cd_c_dx_", i)
  conf_col <- paste0("cd_c_confirmed_", i)
  text_col <- paste0("cd_c_dx_other_", i)
  
  rows_to_update <- FOR[[text_col]] %in% c("LD", "Learning", "learning", "Intellectual", "intellectual", "Fragile", "Dyslexia", "dyslexia", "Dysgraphia", "dysgraphia", "Retardation", "retardation", "Communication", "disability")
  FOR$ccLD[rows_to_update] <- 1
    
  rows_to_update <- FOR[[text_col]] %in% c("Spelling", "spelling", "Reading", "reading", "Non-Verbal", "Processing Speed", "Phonological", "Dyslexia", "dyslexia", "dysgraphia", "Dysgraphia", "Communication") 
  FOR$ccLDs[rows_to_update] <- 1
  
  rows_to_update <- FOR[[text_col]] %in% c("Intellectual", "intellectual", "Retardation", "retardation") 
  FOR$ccLDs[rows_to_update] <- 1
}

#Sleep
FOR$ccSleep <- 0
for (i in 1:10) {
  dx_col <- paste0("cd_c_dx_", i)
  conf_col <- paste0("cd_c_confirmed_", i)
  text_col <- paste0("cd_c_dx_other_", i)
  rows_to_update <- FOR[[text_col]] %in% c("insomnia", "sleep", "somnia")
  FOR$ccSleep[rows_to_update] <- 1
}


#Disruptive Mood
FOR$ccDMDD <- 0
for (i in 1:10) {
  dx_col <- paste0("cd_c_dx_", i)
  conf_col <- paste0("cd_c_confirmed_", i)
  text_col <- paste0("cd_c_dx_other_", i)
  rows_to_update <- FOR[[text_col]] %in% c("DMDD")
  FOR$ccDMDD[rows_to_update] <- 1
}

FOR <- FOR %>%
  mutate(ccMOOD = ifelse(ccBP == 1 | ccDEP == 1 | ccMDD == 1, 1, 0))



for (i in KSADS_ALL) {
  dx_col <- paste0("cc", i)
  
  for (x in 1:16) {
    nxt_col <- paste0(i, "NxtYr", x)
    prv_col <- paste0(i, "PrvYr", x)
    
    FOR <- FOR %>%
      group_by(subject_id) %>%
      arrange(desc(time_point)) %>%
      mutate(
        !!nxt_col := lag(.data[[dx_col]], x),
        !!prv_col := lead(.data[[dx_col]], x)
      ) %>%
      ungroup()
  }
}


for (i in KSADS_ALL) {
  FOR[[paste0("FutureDiag", i)]] <- 0
  FOR[[paste0("PastDiag", i)]] <- 0
}

# Step 2: Loop through each diagnosis and lag/lead year
for (i in KSADS_ALL) {
  for (x in 1:16) {
    dx_Nxt_col <- paste0(i, 'NxtYr', x)
    dx_Prv_col <- paste0(i, 'PrvYr', x)
    future_col <- paste0('FutureDiag', i)
    past_col <- paste0('PastDiag', i)

    # If the future column exists and has value 1
    if (dx_Nxt_col %in% names(FOR)) {
      idx <- which(FOR[[dx_Nxt_col]] == 1)
      FOR[[future_col]][idx] <- 1
    }

    # If the past column exists and has value 1
    if (dx_Prv_col %in% names(FOR)) {
      idx <- which(FOR[[dx_Prv_col]] == 1)
      FOR[[past_col]][idx] <- 1
    }
  }
}

```


###Lifetime Diagnosis
```{r}
###Lifetime Diagnosis
#List of lifetime diagnosis  missing?

#clPBPD, clPDD, clAdjAnx, clPrim

##Mood

for (dx in KSADS_ALL) {
  cc_var <- paste0("cc", dx)
  cl_var <- paste0("cl", dx)

  FOR <- FOR %>%
    group_by(subject_id) %>%
    arrange(assessment_date, .by_group = TRUE) %>%
    mutate(!!cl_var := as.integer(cumsum(.data[[cc_var]] == 1) > 0)) %>%
    ungroup()
}
table(FOR$clMDD)
```


###Onset
```{r}
KSADS <- c('MDD', 'BP', 'BPI', 'BPII', 'MOOD', 'Psychosis', 'SCZ', 'SchAff', 'iPsychosis', 'SUD', 'Alc', 'Can', 'Dependence', 'Anx', 'Panic', 'OthAnx', 'GAD', 'SocialP', 'PTSD', 'Agora', 'OCD', 'SAD', 'ADHD', 'ODD', 'Conduct', 'Disrupt', 'ED', 'EDNOS', 'Anor', 'Bulims', 'Autism', 'ASD', 'Tic', 'Touret', 'LD', 'LDs', 'LDg', 'DMDD', 'Sleep', 'Borderline', 'Antisocial', 'PersonalityDisord')

for (dx in KSADS) {
  cc_var <- paste0("cc", dx)
  o_var <- paste0("o", dx)

  FOR <- FOR %>%
    group_by(subject_id) %>%
    arrange(assessment_date, .by_group = TRUE) %>%
    mutate(!!o_var := ifelse(row_number() == which(.data[[cc_var]] == 1)[1] & time_point >= 2 & .data[[cc_var]] == 1, 1, 0)) %>%
    ungroup()
}
```

###Hospital Diagnosis
```{r}
###  Diagnosis from IWK, notes, conseus

FOR$iid <- as.numeric(FOR$iid)
#Originally ccCan was cannabis, should this be different?
FOR <- FOR %>%
  mutate(
    ccSUD = ifelse(iid == 443 & time_point %in% c(2, 3), 1, ccSUD),
    ccCan = ifelse((iid == 443 & time_point == 3) |
                      (iid == 321 & time_point %in% c(3, 4, 5)), 1, ccCan),
    ccPsychosis = ifelse((iid == 443 & time_point == 3) |
                         (iid == 281 & time_point == 5), 1, ccPsychosis),
    clSUD = ifelse((iid == 321 & time_point == 5) |
                   (iid == 443 & time_point %in% c(2, 3)), 1, clSUD),
    ccBorderline = ifelse(iid == 321 & time_point == 5, 1, ccBorderline),
    clBorderline = ifelse(iid == 321 & time_point == 5, 1, clBorderline),
    ccAntisocial = ifelse(iid == 321 & time_point == 5, 1, ccAntisocial),
    clAntisocial = ifelse(iid == 321 & time_point == 5, 1, clAntisocial),
    clPsychosis = ifelse((iid == 443 & time_point == 3) |
                         (iid == 281 & time_point > 4.5), 1, clPsychosis),
    oSCZ = ifelse((iid == 443 & time_point == 3) |
                   (iid == 281 & time_point == 5), 1, oSCZ)
  )






# ** additional information from IWK, notes, consensusdg
# ** iid 443, transient psychosis, schizoprhenia spectrum disorder, on aripiprazole
# replace ccSUD = 1 if iid==443 & time==2
# replace ccSUD = 1 if iid==443 & time==3
# replace cannabis = 1 if iid==443 & time==3
# replace ccPsychosis=1 if iid==443 & time==3
# replace cannabis = 1 if iid==321 & time==3
# replace cannabis = 1 if iid==321 & time==4
# replace cannabis = 1 if iid==321 & time==5
# replace ccSUD = 1 if iid==321 & time==5
# replace clSUD = 1 if iid==321 & time==5
# replace ccBorderline = 1 if iid==321 & time==5
# replace clBorderline = 1 if iid==321 & time==5
# replace ccAntisocial = 1 if iid==321 & time==5
# replace clAntisocial = 1 if iid==321 & time==5
# 
# replace clSUD = 1 if iid==443 & time==2
# replace clSUD = 1 if iid==443 & time==3
# replace clPsychosis=1 if iid==443 & time==3
# replace oSCHZ=1 if iid==443 & time==3
# replace ccPsychosis=1 if iid==281 & time==5
# replace clPsychosis=1 if iid==281 & time>4.5
# replace oSCHZ=1 if iid==281 & time==5


##Consesus Lifetime Diagnosis
```

# Create my analytic now.
```{r}
setwd("C:/Users/hubshmz/Documents/Code/git/data")  # FORBOW computer
# setwd("C:/Users/zachh/Documents/Code/git/Data")  # Laptop
# setwd("C:/Users/zacha/Documents/RStudio/forbow/git/Data/ESCAP") # Tupper Windows Comp
# setwd("C:/Users/zacha/Documents/forbow/code/git") # Home Computer

write.csv(FOR, file = "analytic-zach.csv", row.names = FALSE)
```


```{r}



```






```{R}
look <- FOR %>% select(subject_id, 'time_point')

FOR <- FOR %>% filter(time_point < 97)

FOR$assessment_date[FOR$assessment_date == ""] <- NA  # Replace "" with NA
FOR$assessment_date <- as.Date(FOR$assessment_date) 



FOR$subject_id <- as.factor(FOR$subject_id)
FOR$assessment_date <- as.Date(FOR$assessment_date)

FOR <- FOR %>%
  arrange(subject_id) %>%
  mutate(
    group_index = (as.integer(subject_id) - 1) %/% 50 + 1,
    group_label = paste0("Group ", group_index)
  )

group_labels <- unique(FOR$group_label)

plot_list <- lapply(group_labels, function(grp) {
  df_grp <- FOR %>% filter(group_label == grp)
  
  p <- ggplot(df_grp, aes(x = assessment_date, y = time_point, group = subject_id, color = subject_id)) +
    geom_line() +
    geom_point(size = 2) +
    theme_minimal() +
    labs(
      title = paste("Participant Timepoints -", grp),
      x = "Assessment Date",
      y = "Timepoint",
      color = "Subject ID"
    )
  
  ggplotly(p)
})

plot_list[[15]]
```



##TOC
```{R}
# 1 "Major Depressive Disorder" ///
# 2 "Dysthymic Disorder" ///
# 3 "Mood Disorder NOS" ///
# 4 "Bipolar disorder I" ///
# 5 "Bipolar disorder II" ///
# 6 "Cyclothymic Disorder" ///
# 7 "Bipolar disorder NOS" ///
# 8 "Schizophrenia" ///
# 9 "Schizoaffective" ///
# 10 "Schizophreniform" ///
# 11 "Delusional Disorder" ///
# 12 "Brief Psychotic Disorder" ///
# 13 "Psychotic Disorder NOS" ///
# 14 "Psychotic disorder substance induced" ///
# 15 "Separation Anxiety" ///
# 16 "Specific Phobia" ///
# 17 "Social Phobia" ///
# 18 "Agoraphobia" ///
# 19 "Panic disorder" ///
# 20 "GAD" ///
# 21 "OCD" ///
# 22 "PTSD" ///
# 23 "Acute Stress" ///
# 24 "Anxiety Disorder NOS" ///
# 25 "Panic Attack" ///
# 26 "Enuresis" ///
# 27 "Encopresis" ///
# 28 "Anorexia Nervosa" ///
# 29 "Bulimia" ///
# 30 "Eating Disorder NOS" ///
# 31 "ADHD Combined" ///
# 32 "ADHD Inattentive" ///
# 33 "ADHD Hyperactive-Imp" ///
# 34 "ODD" ///
# 35 "Conduct Disorder" ///
# 36 "Tic Disorder Chronic" ///
# 37 "Tic Disorder Transient" ///
# 38 "Alcohol Abuse" ///
# 39 "Alcohol Dependence" ///
# 40 "Cannabis abuse" ///
# 41 "Cannabis dependence" ///
# 42 "Substance Abuse" ///
# 43 "Substance Dependence" ///
# 44 "Autistic Disorder" ///
# 45 "Aspergers Disorder" ///
# 46 "PDD NOS" ///
# 98 "Other Disorder" ///
# 99 "No response"


```


