---
title: "Main File for Variable Creation"
output: html_document
date: "2025-11-28"
---
This file is made so that you can create the specific variables you need without having to run an entire script that makes everything. This should output exactly what you need for your analysis. 
---
#
## Library
```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(haven); library(dplyr); library(tidyr); library(readr); library(readxl); library(data.table); library(stringr); library(purrr)  # Data manipulation & import
library(fuzzyjoin)  # Joins

library(zoo)
```

#Load Dataset
Wont work without loading dataset. Go to redcap and pull "ZACH FORBOW Report." Then rename the file so it matches the one below. 

Ensure your WD is set to where you are storing the dataset. 
```{r}
# setwd("C:/Users/hubshmz/Documents/Code/git/data")  # FORBOW computer
setwd("C:/Users/zacha/OneDrive/Documents/Code/Data")  # Laptop
# setwd("C:/Users/zacha/Documents/RStudio/forbow/git/Data/ESCAP") # Tupper Windows Comp
# setwd("C:/Users/zacha/Documents/forbow/code/git") # Home Computer

##Do unlabeled, ZACH FORBOW report from the master database. 
FOR <- read.csv("rawdataforanalysis2.csv", header=TRUE, fileEncoding="latin1")
```


#FHR & Group
This creates:
- FHR: Defined as parental main diagnosis of MDD, BD, or schizophrenia
- Group: 0 = Control, 1 = Parental diagnosis of MDD, 2  Parental Diagnosis of BD, 3 = Parent diagnosis of schiz


TO-DO: Have this also create other parent diagnosis variables
```{r}
source("scripts/Family_Risk_And_Group_Creation.R")
table(FOR$group)

store1 <- c('group', 'fhr')
```

#Demographic Variables
This will create
- Sex
- Race
- Age
- SES
- Pubertal Status (Only Females)
- Whether a pt lives with bio family or not.
```{r}
source("scripts/Demographics.R")
```


#Concurrent Diagnosis, Lifetime, and Hospital Diagnosises 
This has three scripts. 
- Concurrent CONFIRMED CONSESUS diagnosis for the diagnosis available in FORBOW. See the glossary at end for a list
- Lifetime diagnosis diagnosis. This is generated from consesus confirmed diagnosises or from previous confirmed concurrent diagnosises. 
- Hospital Diagnosises. These are diagnoses put in and generated itself.
- Onset. Defined as having a concurrent confiremd diagnosis after baseline. 
```{r}
source("scripts/Concurrent Diagnosis.R")
source("scripts/Lifetime Diagnosis.R")
source("scripts/Hospital Diagnosis.R")
source("scripts/Onset.R")
```

#Maltreatment and Bullying
###Malt variables
Rudolf has ceca/jvq valid for malt creation... isn't in redcap though so unsure

This will generate:
- PolyE 
- Physical, emotional, neglect, custody disruption, sexual, and experienced violent maltreatment variables. 
- Additional generates if any maltreatment was experienced
```{r}
source("scripts/maltreatmentandbullying.R")


#Variables from this
# polye, maltp, malte, maltn, custodydip, malts, maltv.
# malt = experienced any maltp, e, n, or s
# malt b = experienced any malt or maltv
# There are also malt_ever variables, for if someone EVER experienced maltreatment

# Bullying variables, obully, ocyber, and bullying_ever

#Generates polye from adversity/ses info
```


#Dimension Variables
```{r}
#Dimension Depression
source("scripts/dimdep.R")

#dimension Anxiety
source("scripts/dimanx.R")

```

#Glossary
##Diagnosises in FORBOW
```{R}
# 1 "Major Depressive Disorder" ///
# 2 "Dysthymic Disorder" ///
# 3 "Mood Disorder NOS" ///
# 4 "Bipolar disorder I" ///
# 5 "Bipolar disorder II" ///
# 6 "Cyclothymic Disorder" ///
# 7 "Bipolar disorder NOS" ///
# 8 "Schizophrenia" ///
# 9 "Schizoaffective" ///
# 10 "Schizophreniform" ///
# 11 "Delusional Disorder" ///
# 12 "Brief Psychotic Disorder" ///
# 13 "Psychotic Disorder NOS" ///
# 14 "Psychotic disorder substance induced" ///
# 15 "Separation Anxiety" ///
# 16 "Specific Phobia" ///
# 17 "Social Phobia" ///
# 18 "Agoraphobia" ///
# 19 "Panic disorder" ///
# 20 "GAD" ///
# 21 "OCD" ///
# 22 "PTSD" ///
# 23 "Acute Stress" ///
# 24 "Anxiety Disorder NOS" ///
# 25 "Panic Attack" ///
# 26 "Enuresis" ///
# 27 "Encopresis" ///
# 28 "Anorexia Nervosa" ///
# 29 "Bulimia" ///
# 30 "Eating Disorder NOS" ///
# 31 "ADHD Combined" ///
# 32 "ADHD Inattentive" ///
# 33 "ADHD Hyperactive-Imp" ///
# 34 "ODD" ///
# 35 "Conduct Disorder" ///
# 36 "Tic Disorder Chronic" ///
# 37 "Tic Disorder Transient" ///
# 38 "Alcohol Abuse" ///
# 39 "Alcohol Dependence" ///
# 40 "Cannabis abuse" ///
# 41 "Cannabis dependence" ///
# 42 "Substance Abuse" ///
# 43 "Substance Dependence" ///
# 44 "Autistic Disorder" ///
# 45 "Aspergers Disorder" ///
# 46 "PDD NOS" ///
# 98 "Other Disorder" ///
# 99 "No response"
```

