---
title: "Main File for Variable Creation"
output: html_document
date: "2025-11-28"
---
This file is made so that you can create the specific variables you need without having to run an entire script that makes everything. This should output exactly what you need for your analysis. 
---
#1. Setup ------------------------------
###1.1 Library
```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(haven); library(dplyr); library(tidyr); library(readr); library(readxl); library(data.table); library(stringr); library(purrr)  # Data manipulation & import

library(zoo)
library(lubridate)
```

###1.2 Load Dataset
Wont work without loading dataset. Go to redcap and pull "ZACH FORBOW Report." Then rename the file so it matches the one below. 

Ensure your WD is set to where you are storing the dataset. 
```{r}
#wd <- "C:/Users/hubshmz/Documents/Code/git/data"  # FORBOW computer
wd <- "C:/Users/zacha/OneDrive/Documents/Code/Data"  # Laptop
#wd <- "C:/Users/zacha/Documents/RStudio/forbow/git/Data/ESCAP" # Tupper Windows Comp
#wd <- "C:/Users/zacha/Documents/forbow/code/git" # Home Computer

##Do unlabeled, ZACH FORBOW report from the master database. 

setwd(wd)
FOR <- read.csv("rawdataforanalysis.csv", header=TRUE, fileEncoding="latin1")

#Do unlabeled, all data from RMU2012_010 -FORBOW redcap.
FORredcap <- read.csv("rawdataforanalysis2.csv", header=TRUE, fileEncoding="latin1")
```

###1.3 Merge Databases
This probably successfully merges but double check later.
```{r}
source("scripts/demographic/mergedatabase.R")
#This has around 70 or so people that arent joined properly. Investigate at some point. 
#Tthis las
```


#2.0 Participant Information------------
###2.1 FHR & Group
This creates:
- FHR: Defined as parental main diagnosis of MDD, BD, or schizophrenia
- Group: 0 = Control, 1 = Parental diagnosis of MDD, 2  Parental Diagnosis of BD, 3 = Parent diagnosis of schiz


TO-DO: Have this also create other parent diagnosis variables
```{r}
source("scripts/demographic/Family_Risk_And_Group_Creation.R")
table(FOR$group)

store1 <- c('group', 'fhr')
```

###2.2 Demographic Variables
This will create
- Sex (0 = Male, 1 = Female)
- Race 
- Age
- SES 
- Pubertal Status (Only Females)
- Bio family at home (0 = doesnt live with bio fam, 1 = lives with bio fam)
```{r}
source("scripts/demographic/Demographics.R")
```

###2.3 Meds
WIP


#3.0 Diagnosis and Psychopathology -------
###3.1 Diagnosis
####3.1.1 Concurrent
Concurrent CONFIRMED CONSESUS diagnosis for the diagnosis available in FORBOW. See the glossary at end for a list
```{r}
source("scripts/Diagnosis/Concurrent Diagnosis.R")
```
####3.1.2 Lifetime
Lifetime diagnosis diagnosis. This is generated from consensus confirmed diagnoses or from previous confirmed concurrent diagnoses. 
```{r}
source("scripts/Diagnosis/Lifetime Diagnosis.R")
```
####3.1.3 Onset
Onset. Defined as having a concurrent confirmed diagnosis after baseline.
```{r}
source("scripts/Diagnosis/Onset.R")
```
####3.1.4 Hospital Diagnosises 
Hospital Diagnoses. These are diagnoses put in and generated itself.
```{r}
source("scripts/Diagnosis/Hospital Diagnosis.R")
```


###4.0 Psychopathology-----------------
####4.1 Maltreatment and Bullying

CODER NOTES: Rudolf has ceca/jvq valid for malt creation... isn't in redcap though so unsure

This will generate:
- PolyE 
- Physical, emotional, neglect, custody disruption, sexual, and experienced violent maltreatment variables. 
- Additional generates if any maltreatment was experienced
- Bullying variables: Obully, ocyber, bullying_ever
```{r}
source("scripts/maltreatmentandbullying.R")
```

####4.2 FORBOW Measures

#####4.2.1 Yeti
```{r}
source("scripts/Measures/yeti.R")
```

#####4.2.2 MFQ
Generates mfqptot and mfqytot. Totals of youth/parent scoring of MFQ
This also has imputation in it using median.
```{r}
source("scripts/Measures/mfq.R")
```

#####4.2.3 Scared
Generates scared total from youth and parent. 
```{r}
source("scripts/Measures/scared.R")
```

#####4.2.4 Scas
Generates scas total from youth and parent.
```{r}
source("scripts/Measures/scas.R")
```

#####4.2.5 CSHQ
Generate CSHQ total.
Needs subscales added in.
```{r}
source("scripts/Measures/cshq.R")
```


#####4.2.6 PSQI
Generates a PSQI total score.
Generates subscales:
- Efficiency
- Quality
- Sleep Onset Latency
- Sleep disturbances
- Medication Use for Sleep
- Daytime Sleepinesss

CODER NOTE: Working on PSQI: Need to fix SE
------PSQI is extremely messy data.-----
A LOT OF WRONG INPUTS ON PSQI
NEEDS MANUALLY FIXING
```{r}
source("scripts/Measures/psqi.R")
```

#####4.2.7 SSH
```{r}
source("scripts/Measures/SSH.R")
```

#####4.2.8 SSR


#####4.2.9 Choci
```{r}
source("scripts/Measures/CHOCI.R")
```

#####4.2.10 OCI
Generates OCI_Total
Sub scales Generated:
- Obsessions 
- Washing 
- Checking
- Hoarding
- Doubting
- Neutral
- Order
```{r}
source("scripts/Measures/OCI.R")
```




####4.3 Dimension Variables
dimbs, dimirrit, dimafflab
#####4.3.1 Dimdep
Generates dimdep - Made up of zMFQytot and zMFQptot
```{r}
#Dimension Depression
source("scripts/standarized scale harmonized scores/dimdep.R")
```

#####4.3.2 Dimanx
Generates dimanx - Made up of zSCAREDytot, zSCAREDptot, zSCASytot, and zSCASptot
```{r}
#dimension Anxiety
source("scripts/standarized scale harmonized scores/dimanx.R")
```

#####4.3.3 Sleep
Geneates dim sleep - Made up of zCSH, zPSQI, zSSH, and zSSR scores.

CODER NOTE: Working on PSQI: Need to fix SE
------PSQI is extremely messy data.-----
A LOT OF WRONG INPUTS ON PSQI

```{r}
#Dimension Sleep
source("scripts/standarized scale harmonized scores/dimsleep.R")
```

#####4.3.4 Psych
This requires something from rudolf, has to do with curated PLEs

#####4.3.5 OCD
Generates dimocd - Made up of zCHOCIptot, zCHOCIytot, and zOCI.
```{r}
#Dimension OCD
#Id double check this script probably.
source("scripts/standarized scale harmonized scores/dimocd.R")
```

#####4.3.6 Affective Lability
```{r}
#Dimension affect Lability
source("scripts/standarized scale harmonized scores/dimal.R")
```


####4.4 Antecedents
#####4.4.1 Dimdep
Generates dimdep - If ccMDD or ccDEP == 1 then dimdep == 1. If MFQy or MFQp > 8.5 then dimdep == 1. 
```{r}
source("scripts/dimensions/dimdep.R")
sum(FOR$ccMDD == 1, na.rm = TRUE)
sum(FOR$ccDEP == 1, na.rm = TRUE)
sum(FOR$mfqytot > 8.5, na.rm = TRUE)
sum(FOR$mfqptot > 8.5, na.rm = TRUE)
```

#####4.4.2 Dim


#10.0 Output
##10.1 Output Everything
```{r}
setwd(wd)
write.csv(FOR, file = "analytic-zach.csv", row.names = FALSE)
```

##10.2 Output what scripts you ran
```{r}
#WIP
```

#Glossary
##Diagnosises in FORBOW
```{R}
# 1 "Major Depressive Disorder" ///
# 2 "Dysthymic Disorder" ///
# 3 "Mood Disorder NOS" ///
# 4 "Bipolar disorder I" ///
# 5 "Bipolar disorder II" ///
# 6 "Cyclothymic Disorder" ///
# 7 "Bipolar disorder NOS" ///
# 8 "Schizophrenia" ///
# 9 "Schizoaffective" ///
# 10 "Schizophreniform" ///
# 11 "Delusional Disorder" ///
# 12 "Brief Psychotic Disorder" ///
# 13 "Psychotic Disorder NOS" ///
# 14 "Psychotic disorder substance induced" ///
# 15 "Separation Anxiety" ///
# 16 "Specific Phobia" ///
# 17 "Social Phobia" ///
# 18 "Agoraphobia" ///
# 19 "Panic disorder" ///
# 20 "GAD" ///
# 21 "OCD" ///
# 22 "PTSD" ///
# 23 "Acute Stress" ///
# 24 "Anxiety Disorder NOS" ///
# 25 "Panic Attack" ///
# 26 "Enuresis" ///
# 27 "Encopresis" ///
# 28 "Anorexia Nervosa" ///
# 29 "Bulimia" ///
# 30 "Eating Disorder NOS" ///
# 31 "ADHD Combined" ///
# 32 "ADHD Inattentive" ///
# 33 "ADHD Hyperactive-Imp" ///
# 34 "ODD" ///
# 35 "Conduct Disorder" ///
# 36 "Tic Disorder Chronic" ///
# 37 "Tic Disorder Transient" ///
# 38 "Alcohol Abuse" ///
# 39 "Alcohol Dependence" ///
# 40 "Cannabis abuse" ///
# 41 "Cannabis dependence" ///
# 42 "Substance Abuse" ///
# 43 "Substance Dependence" ///
# 44 "Autistic Disorder" ///
# 45 "Aspergers Disorder" ///
# 46 "PDD NOS" ///
# 98 "Other Disorder" ///
# 99 "No response"
```

